\Large \bf On semidefinite-representable sets over valuation fields

### 2025-05-22 article/paper_padic_spec.tex
modif abstract
commit by Simone

%\title{\bf Title}
%\title{\bf On polyhedra and spectrahedra over valuation fields}
\title{\bf On semidefinite-representable sets over valuation fields}

@@

In this paper we 
Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral}.

>>>>

%\title{\bf Title}
%\title{\bf On polyhedra and spectrahedra over valuation fields}
\title{\Large \bf On semidefinite-representable sets over valuation fields}

@@

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. The main example is the field of $p$-adic numbers with $p$-adic valuation. Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving}.
